Manuscript 1 code

### 2024-09-11 manuscript_1_code.Rmd
fixed legend and colors (please make colors pretty)

functional_group_colours <- c("coral" = "darkmagenta",
                         "cca" = "pink",
                         "macroalgae" = "#004D40",
                         "turf" =  "#1E88E5")

@@

#make levels for habitat for plotting
cover_long$habitat <- factor(cover_long$habitat, 
                             levels = c("fringing", "backreef", "outer_10","outer_17"),
                             labels = c("Fringing", "Backreef", "Forereef 10m", "Forereef 17m"))
```

@@

```{r figure 1, fig.height = 10, fig.width=14}
(figure_1 <- ggplot(data = subset(cover_long, functional_group != "sand" & functional_group != "other")) +
  geom_line(aes(x = year, y = percent_cover, colour = functional_group), linewidth = 1) +
  geom_ribbon( aes(x = year, ymin = percent_cover - se, ymax = percent_cover + se, fill = functional_group), alpha = 0.3) +
  facet_wrap(~ habitat) +
  geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  scale_colour_manual(values = functional_group_colours) +
  scale_fill_manual(values = functional_group_colours) +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(cover_long$year)) +
   labs(y = "Percent Cover \n",
        x = "Year") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )

>>>>

functional_group_colours <- c("Coral" = "darkmagenta",
                         "CCA" = "deeppink3",
                         "Macroalgae" = "#004D40",
                         "Turf" =  "chartreuse4")

@@

#make levels for habitat for plotting
cover_long$habitat <- factor(cover_long$habitat, 
                             levels = c("fringing", "backreef", "outer_10","outer_17"),
                             labels = c("Fringing", "Backreef", "Forereef 10m", "Forereef 17m"))

cover_long$functional_group <- factor(cover_long$functional_group, 
                             levels = c("macroalgae", "coral", "turf","cca", "sand", "other"),
                             labels = c("Macroalgae", "Coral", "Turf", "CCA", "Sand", "Other"))
```

@@

```{r figure 1, fig.height = 10, fig.width=14}
(figure_1 <- ggplot(data = subset(cover_long, functional_group != "Sand" & functional_group != "Other")) +
  geom_line(aes(x = year, y = percent_cover, colour = functional_group), linewidth = 1) +
  geom_ribbon( aes(x = year, ymin = percent_cover - se, ymax = percent_cover + se, fill = functional_group), alpha = 0.3) +
  facet_wrap(~ habitat) +
  geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  scale_colour_manual(values = functional_group_colours) +
  scale_fill_manual(values = functional_group_colours) +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(cover_long$year)) +
   labs(y = "Percent Cover \n",
        x = "Year") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )
